---
title: "2021_03_03_MarkDownGroup"
author: "Anthony Gutierrez"
date: "3/3/2021"
output:  
  rmdformats::readthedown

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message=FALSE,
                      warning=FALSE,
                      fig.path="../outputs/")
```


# Introdction 
Today we are working as a group to make some beautiful grapghs and figures on MarkDown


## Load Libraries 
```{r}
library(palmerpenguins)
library(tidyverse)
library(here)
library(kableExtra)
library(ggbernie)
library(rmdformats)

view(penguins)
```


## Lab Assignment
- Take any of the data sheets you have already worked with in class and create at least one table and one figure in an Rmarkdown file.  
- Create the most beautiful RMarkdown output you can during lab hours in either an html, github doc, or pdf format.    
- Make sure you have headings with clear explanations of what you are doing.  
- Practice using markdown formatting with bold, italics, and lists.    
- Make sure your outputs and scripts are saved in the appropriate folders. Keep proper coding etiquette (figures need to be pub quality as usual).  


### Create table 
```{r}
penguins %>%
  group_by(species, island, year) %>%
  summarise(mean_mass = mean(body_mass_g, na.rm=TRUE),
  mean_flipper = mean(flipper_length_mm, na.rm=TRUE))%>%
  kbl() %>%
  kable_classic() %>%
  row_spec(0, bold=T)
  
```

### plot 
```{r, Penfig, fig.width=7, fig.height=5, fig.align='center', fig.cap= "penguin body mass"}
PenguinFigures<- penguins %>%
  ggplot(aes(x = flipper_length_mm,
             y= body_mass_g,
             group = species,
             color = island))+
  geom_boxplot()
PenguinFigures
```

