---
title: "Better graph"
author: "Anthony Gutierrez"
date: "3/21/2021"
output:
  html_document:
    df_print: paged
---

# Introduction
The goal in this part is to make the best possible figure

```{r}
knitr::opts_chunk$set(echo = TRUE,
                      fig.path="../outputs/")
```

# Load Libraries 
```{r setup, include=FALSE}
library(tidyverse)
library(palmerpenguins)
library(here)
library(rmdformats)
library(kableExtra)
knitr::opts_chunk$set(echo = TRUE)

view(penguins)
```


```{r, Penfig, fig.width=7, fig.height=5, fig.align='center', fig.cap= "Penguin bill measurements"}
PenguinFigures<- penguins %>%
  group_by(species)%>%
  ggplot(aes(x = bill_length_mm, y = bill_depth_mm, color = species))+
  geom_point()+
  scale_color_viridis_d() +
  geom_smooth(method = "lm")+ #linear model
  labs(x = "Bill Length (mm)",
       y = "Bill Depth (mm)",
       title = "Penguin bill measurements by species")+
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(face="bold", size=15), 
        plot.title = element_text(face = "bold"))
  

PenguinFigures

```

# Explanation why the graph is presentable and acceptable
Title clearly exaplins the content and is a good font size  
Axis lablels include units and have a good font size   
Clear that this figure groups by species. Species is color coated  
Well defined legend  
Used color blind - friendly colors

