---
title: "Bad graph"
author: "Anthony Gutierrez"
date: "3/21/2021"
output: html_document
---

# Introduction
The goal in this part is to make the worst possible figure

```{r}
knitr::opts_chunk$set(echo = TRUE,
                      fig.path="../outputs/")
```

# Load Libraries 
```{r setup, include=FALSE}
library(tidyverse)
library(palmerpenguins)
library(here)
library(rmdformats)
library(kableExtra)
library(ggbernie)
knitr::opts_chunk$set(echo = TRUE)

view(penguins)
```

```{r}
penguins_name<- penguins %>%
  rename("birdtype" = species)

penguins_name
```

```{r, Penfig, fig.width=7, fig.height=5, fig.align='center', fig.cap= "the bird noses"}
PenguinFigures2<- penguins_name %>%
  ggplot(aes(x = bill_length_mm, y = bill_depth_mm, color = birdtype))+
  geom_bernie(aes(x = bill_length_mm, y = bill_depth_mm), bernie = "sitting")+
  geom_boxplot() + #linear model
  labs(x = "length ",
       y = "depth",
       title = "noses")+
  geom_jitter(color="black", size=0.4, alpha=0.9) +
  scale_color_grey()+
  theme_bw()+
  theme(strip.text = element_text(face="bold", size=1000), 
        plot.title = element_text(face = "bold"))

```

## Change font size
```{r}
one<- PenguinFigures2 + theme(axis.text = element_text(size = 30))

Final<- one + theme(axis.title = element_text(size = 5))
Final
```

# Explanation why the graph is not presentable or acceptable
Unclear title does not define what is being presented well. It is unclear that we are comparing bill length and depth of penguin species.  
Axis titles are too small, axis numbers are too large.  
Box plot is not an appropriate statistical analysis for this particular datset.   
Data points were replaced by Bernie's, which makes the figure look very cluttered and is distracting.   
Species are not color coated, so there is no way to differentiate between points.  
Legend is unclear. It is not clear that Birdtype is species of penguin. Legend colors are very similar. 
