---
title: "Patchwork"
author: "Anthony Gutierrez"
date: "3/28/2021"
output:
  html_document:
    df_print: paged
---

# Introduction
We will be learning how to use a few new R packages.  
{patchwork} - bringing plots together  
{ggrepel} - repel your labels on your plots  
{gganimate} - add some animations to your plots  
{magick} - photo processing  

#Load Libraries 
```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(patchwork)
library(ggrepel)
library(gganimate)
library(magick)
library(palmerpenguins)
knitr::opts_chunk$set(echo = TRUE)
```

#Plotting 
##Plotting with Patchwork
```{r}
# plot 1
p1<-penguins %>%
  ggplot(aes(x = body_mass_g, 
             y = bill_length_mm, 
             color = species))+
  geom_point()

p1

# plot 2
p2<-penguins %>%
  ggplot(aes(x = sex, 
             y = body_mass_g, 
             color = species))+
  geom_jitter(width = 0.2)

p2
```

Put one plot on top of the other.
```{r}
#Patchwork in action

p1+p2 + #Bring the plots together using simple operations.
  plot_layout(guides = 'collect')+ #Group the legends.
  plot_annotation(tag_levels = 'A') #Add labels (A,B).
```

## Plotting with ggrepel 
```{r}
View(mtcars)

#ggplot(mtcars, aes(x = wt, 
#                   y = mpg, 
#                   label = rownames(mtcars))) +
#  geom_text() + # creates a text label
#  geom_point(color = 'red')

#Repel the labels 
#ggplot(mtcars, aes(x = wt, 
#                   y = mpg, 
#                   label = rownames(mtcars))) +
#  geom_text_repel() + # repel them
#  geom_point(color = 'red')

#Label the text
ggplot(mtcars, aes(x = wt, 
                   y = mpg, 
                   label = rownames(mtcars))) +
  geom_label_repel() + # repel them
  geom_point(color = 'red')
```

## Plotting with gganimate 
```{r}

#Add transition to normal plot
penguins %>%
ggplot(aes(x = body_mass_g, 
            y = bill_depth_mm, 
            color = species)) +
  geom_point() +
  transition_states(
     year, # what are we animating by
     transition_length = 2, #The relative length of the transition.
     state_length = 1 # The length of the pause between transitions
   )+
  ease_aes("bounce-in-out")+ #Change the ease aesthetics 
  ggtitle('Year: {closest_state}')+ #Add transition title
  anim_save(here("week_9","outputs","mypengiungif.gif"))
```

## Plotting with magick
magick is used for advanced image processing 
```{r}
#Read in an image of a pengiun (can be on your computer or the internet).
penguin<-image_read("https://pngimg.com/uploads/penguin/pinguin_PNG9.png")

penguin

#To put it on a plot you first need to save your plot as an image.
penguins %>%
ggplot(aes(x = body_mass_g, 
            y = bill_depth_mm, 
            color = species)) +
  geom_point() +
  ggsave(here("week_9","outputs","penguinplot.png"))
```

Read in the plot as a magick image and make a composite plot
```{r}
penplot<-image_read(here("week_9","outputs","penguinplot.png"))
out <- image_composite(penplot, penguin, offset = "+70+30")

out

#You can do this with gifs too!!!
# Read in a penguin gif
pengif<-image_read("https://media3.giphy.com/media/H4uE6w9G1uK4M/giphy.gif")
outgif <- image_composite(penplot, pengif, gravity = "center")
animation <- image_animate(outgif, fps = 10, optimize = TRUE)

animation
```

