---
title: "Group_Function_Writing"
author: "Anthony Gutierrez"
date: "3/24/2021"
output:  
  rmdformats::readthedown
---
# NEED TO CHANGE HTML OUTPUT SO THAT IT SHOWS LIBRARY
# Introduction
Description: Use any of the datasets that we have used in class and make two useful functions. One that is a plot and one that is not. Turn in your functions using RMarkdown with at least 2 examples each showing its flexibility. Due, as always, at 9am on Monday.

I will be making to plots for the sake of prctice. 

# Load Libraries 
```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(PNWColors) # for the PNW color palette 

ChemData<- read_csv(here("week_9", "data", "chemicaldata_maunalua.csv"))
View(ChemData) #The data set I am using 

```

# Changing Temperature Function 
```{r}
#This is a function changing celcuis to Farenheit 
celcius_to_Ferenheit <- function(temp_C) { 
  temp_F <- (temp_C *9/5) +32 
  return(temp_F)
}
#Test Function
celcius_to_Ferenheit(100)
```

# Plotting 

Linear Plot
```{r}
pal <- pnw_palette("Lake",3, type = "discrete") # my color palette  
myplot <- function(data = ChemData, x, y){
pal<-pnw_palette("Lake",3, type = "discrete") # my color palette 
ggplot(data, aes(x = {{x}}, y = {{y}} , color = Site))+
  geom_point()+
  geom_smooth(method = "lm")+ # add a linear model
  scale_color_manual("Site", values=pal)+   # use pretty colors and change the legend title
  theme_bw()
}

#Chaning to appropriate labels
myplot(x = Season, y = celcius_to_Ferenheit(Temp_in))+
    labs(x = "Season",
       y = "Temperature (F)")

```

Box Plot
```{r}
pal <- pnw_palette("Lake",3, type = "discrete") # my color palette  
myplot <- function(data = ChemData, x, y){
pal<-pnw_palette("Lake",3, type = "discrete") # my color palette 
ggplot(data, aes(x = {{x}}, y = {{y}} , color = Site))+
  geom_boxplot()+
  geom_jitter()+
  scale_color_manual("Site", values=pal)+   # use pretty colors and change the legend title
  theme_bw()
}

#Chaning to appropriate labels
myplot(x = Season, y = celcius_to_Ferenheit(Temp_in))+
    labs(x = "Season",
       y = "Temperature (F)")

```

