---
title: "Functional Programming"
author: "Anthony Gutierrez"
date: "3/24/2021"
output: html_document
---
# Introduction 
Today we are learning to write custom funtions instead of using canned functions. 
If you have a function that you use a lot, consider putting it at the top of the script for reference and ease of access.  


# Load libraries
```{r setup, include=FALSE}
library(tidyverse)
library(palmerpenguins)
library(PNWColors) # for the PNW color palette 
knitr::opts_chunk$set(echo = TRUE)
```


# Create First Function
```{r}
df <- tibble::tibble(
  a = rnorm(10), # draws 10 random values from a normal distribution
  b = rnorm(10),
  c = rnorm(10),
  d = rnorm(10)
)

df<-df %>%
  mutate(a = (a-min(a, na.rm = TRUE))/(max(a, na.rm = TRUE)-min(a, na.rm = TRUE)))

df<-df %>%
  mutate(a = (a-min(a, na.rm = TRUE))/(max(a, na.rm = TRUE)-min(a, na.rm = TRUE)),
         b = (b-min(b, na.rm = TRUE))/(max(b, na.rm = TRUE)-min(b, na.rm = TRUE)),
         c = (c-min(c, na.rm = TRUE))/(max(c, na.rm = TRUE)-min(c, na.rm = TRUE)),
         d = (d-min(d, na.rm = TRUE))/(max(d, na.rm = TRUE)-min(d, na.rm = TRUE)))
```

## How to Avoid Errors
```{r}
rescale01 <- function(x) { #x is argument name. code you have developed goes in the brackets. 
  value<-(x-min(x, na.rm = TRUE))/(max(x, na.rm = TRUE)-min(x, na.rm = TRUE))
  return(value)
}
df %>%
  mutate(a = rescale01(a),
         b = rescale01(b),
         c = rescale01(c),
         d = rescale01(d))
```

## Temperature conversion 
```{r}
temp_C <- (temp_F - 32) * 5 / 9 #This is the calculation 
fahrenheit_to_celcius <- function(temp_F) #Name of function. In parenthasis is the argument
{temp_C <- (temp_F - 32) * 5 / 9 } #Put in equation

fahrenheit_to_celsius <- function(temp_F) { 
  temp_C <- (temp_F - 32) * 5 / 9 
  return(temp_C)}
```

```{r}
celcius_to_kelvin <- function(temp_C) { 
  temp_K <- (temp_C + 273.15) 
  return(temp_K)
  }

celcius_to_kelvin(100)





celcius_to_kelvin <- function(temp_C){
  temp_k <- (temp_C + 273.15)
  return(temp_k)
}
celcius_to_kelvin(10)
```

#Making a plot
```{r}
pal <- pnw_palette("Lake",3, type = "discrete") # my color palette  

ggplot(penguins, aes(x = body_mass_g, y = bill_length_mm, color = island))+
  geom_point()+
  geom_smooth(method = "lm")+ # add a linear model
  scale_color_manual("Island", values=pal)+   # use pretty colors and change the legend title
  theme_bw()
```
## Name and Set up Function
```{r}
myplot1<-function(data, x, y){
pal<-pnw_palette("Lake",3, type = "discrete") # my color palette 

ggplot(data, aes(x = x, y =y , color = island))+
  geom_point()+
  geom_smooth(method = "lm")+ # add a linear model
  scale_color_manual("Island", values=pal)+   # use pretty colors and change the legend title
  theme_bw()
}
myplot1(data = penguins, x = body_mass_g, y = bill_length_mm)
# This code should not work
```

```{r}
#Function should work after adding curly bracets around the "x" and "y".
myplot2<-function(data, x, y){ 
pal<-pnw_palette("Lake",3, type = "discrete") # my color palette 
ggplot(data, aes(x = {{x}}, y = {{y}} , color = island))+
  geom_point()+
  geom_smooth(method = "lm")+ # add a linear model
  scale_color_manual("Island", values=pal)+   # use pretty colors and change the legend title
  theme_bw()
}

myplot2(data = penguins, x = body_mass_g, y = bill_length_mm)

#Test with variables
myplot2(data = penguins, x = body_mass_g, y = flipper_length_mm)
```

Adding Defaults 
```{r}
myplot3<-function(data = penguins, x, y){
pal<-pnw_palette("Lake",3, type = "discrete") # my color palette 
ggplot(data, aes(x = {{x}}, y = {{y}} , color = island))+
  geom_point()+
  geom_smooth(method = "lm")+ # add a linear model
  scale_color_manual("Island", values=pal)+   # use pretty colors and change the legend title
  theme_bw()
}


myplot3(x = body_mass_g, y = flipper_length_mm)+
  labs(x = "Body mass (g)",
       y = "Flipper length (mm)")
```

# if-else statements 
```{r}
a <- 4
b <- 5

# Suppose that if a > b then f should be = to 20, else f should be equal to 10. Using if/else we:
if (a > b) { # my question
  f <- 20 # if it is true give me answer 1
    } else { # else give me answer 2
  f <- 10
}

f
```

If-else plot
```{r}

myplot<-function(data = penguins, x, y, lines=TRUE ){ # add new argument for lines
pal<-pnw_palette("Lake",3, type = "discrete") # my color palette 
if(lines==TRUE){
ggplot(data, aes(x = {{x}}, y = {{y}} , color = island))+
  geom_point()+
  geom_smooth(method = "lm")+ # add a linear model
  scale_color_manual("Island", values=pal)+   # use pretty colors and change the legend title
  theme_bw()
}
else{
ggplot(data, aes(x = {{x}}, y = {{y}} , color = island))+
  geom_point()+
  scale_color_manual("Island", values=pal)+   # use pretty colors and change the legend title
  theme_bw()
}
}

myplot(x = body_mass_g, y = flipper_length_mm)

#Without lines
myplot(x = body_mass_g, y = flipper_length_mm, lines = FALSE)
```

# Today's totally awesome R package
```{r}
library(fortunes)
fortune()
```
