---
title: "worldmap"
author: "Anthony Gutierrez"
date: "3/21/2021"
output: html_document
---

# Load Libraries 
```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(maps)
library(mapdata)
library(mapproj)
knitr::opts_chunk$set(echo = TRUE,
                      warning=FALSE,
                      message=FALSE)
```

# Read in data on population in Cali by county
```{r}
popdata<- read_csv(here("week_7", "data", "CAPopdata.csv"))
```

```{r}
stars<- read_csv(here("Week_7","data","stars.csv"))

world<- map_data("world") #get geographical image of the selected area. 
head("world")

usa<- map_data("usa")
head(usa)

italy<- map_data("italy")
head(italy)

states<- map_data("state")
head(states)

counties<- map_data("county")
counties

```

## Nomenclature
long= longitude
lat= latitude
order= in what order ggplot should connect dts
region or subregions
group= controls whether adjacent points should be cnnected by lines 

```{r}
ggplot()+
  geom_polygon(data = world, 
               aes(x = long, #coordinates 
                   y = lat, 
                   group = group,
                   fill = region), # fill in area 
               color = "black")+ # olor of the outline
  theme_minimal()+
  guides(fill = FALSE)+
  theme(panel.background = element_rect(fill = "lightblue"))+
  coord_map(projection = "mercator", # note: many different types of projection
            xlim = c(-180,180))
```


# Filter out just Cali
```{r}
CA_data <- states %>%
  filter(region == "california")

# Use the states dataset
ggplot()+
geom_polygon(data = CA_data, 
             aes(x = long, 
                 y = lat, 
                 group = group), 
             color = "black")+ #black outline 
  coord_map()+
  theme_void()# black fill in 
```
# Adding multiple layers of data

First we need to get the country level data and join it with our dataset on population 

```{r}
CApop_county<-popdata %>%
  select("subregion" = County, Population)  %>% # rename the county col
  inner_join(counties) %>%
  filter(region == "california") # some counties have same names in other states

view(CApop_county)

head(CApop_county)

ggplot()+
geom_polygon(data = CApop_county, 
             aes(x = long, 
                 y = lat, 
                 group = group,
                 fill = Population),  
             color = "black")+
  geom_point(data = stars, # add a point at all my sites 
             aes(x = long, 
                 y = lat,
                 size = star_no))+ 
  coord_map()+
  theme_void() +
  scale_fill_gradient(trans = "log10")+
  labs(size = "# stars/m2") + #adding legend for the star size
  ggsave(here("week_7","outputs","CApop.pdf"))
```

