---
title: "Models"
author: "Anthony Gutierrez"
date: "4/28/2021"
output: html_document
---

# Libraries 

```{r}
library(tidyverse)
library(here)
library(palmerpenguins)
library(broom)
library(performance) # if you didn't already install from group projects install it
library(modelsummary)
library(tidymodels)
```

# Intro to basic linear modeling 
I am going to show you a few cool packages that help with some modeling

# Anatomy of a basic linear model
To run a simple linear model you use the following formula:

mod<-lm(y~x, data = df)

lm = linear model, y = dependent variable, x = independent variable(s), df = dataframe.

You read this as y is a function of x

Multiple regression
mod<-lm(y~x1 + x2, data = df)

Interaction term
mod<-lm(y~x1*x2, data = df) the * will compute x1+x2+x1:x2


# Model the penguin dataset 
```{r}
# Linear model of Bill depth ~ Bill length by species
Peng_mod<-lm(bill_length_mm ~ bill_depth_mm*species, data = penguins)

Peng_mod

check_model(Peng_mod) # check assumptions of an lm model 

anova(Peng_mod)

summary(Peng_mod)# Coefficients (effect size) with error
```

# View Results with Broom 

```{r}
# Tidy coefficients
coeffs<-tidy(Peng_mod) # just put tidy() around it
coeffs



# tidy r2, etc
results<-glance(Peng_mod) 
results



# tidy residuals, etc
resid_fitted<-augment(Peng_mod)
resid_fitted
```



# Results is {modelsummary}
{modelsummary} creates tables and plots to summarize statistical models and data in R.

```{r}
# New model
Peng_mod_noX<-lm(bill_length_mm ~ bill_depth_mm, data = penguins)
#Make a list of models and name them
models<-list("Model with interaction" = Peng_mod,
             "Model with no interaction" = Peng_mod_noX)
#Save the results as a .docx
modelsummary(models, output = here("week_13","outputs","table.docx"))
```



# Modelplot
```{r}
library(wesanderson)
modelplot(models) +
    labs(x = 'Coefficients', 
         y = 'Term names') +
    scale_color_manual(values = wes_palette('Darjeeling1'))
```


# Many models with purrr, dplyr, and broom

```{r}
 models<- penguins %>%
  ungroup()%>% # the penguin data are grouped so we need to ungroup them
  nest(-species) %>% # nest all the data by species 
  mutate(fit = map(data, ~lm(bill_length_mm~body_mass_g, data = .)))

  models
```


```{r}
 results<-models %>%
   mutate(coeffs = map(fit, tidy), # look at the coefficients
          modelresults = map(fit, glance)) %>% # R2 and others 
   select(species, coeffs, modelresults) %>% # only keep the results
   unnest() # put it back in a dataframe and specify which columns to unnest

view(results) # view the results

```


# Tiny Models

function: 'linear_reg()'
```{r}
lm_mod<-linear_reg() %>%
  set_engine("lm") %>%
  fit(bill_length_mm ~ bill_depth_mm*species, data = penguins) %>%
  tidy() %>%
  ggplot()+
    geom_point(aes(x = term, y = estimate))+
    geom_errorbar(aes(x = term, ymin = estimate-std.error,
                      ymax = estimate+std.error), width = 0.1 )+
  coord_flip()


lm_mod
```



# Totally Aewsome R package 
{pushoverr}: Send push notifications to your phone from R! Does your code take forever to run and you want to go on a run yourself? Have it send your phone or smartwatch a push notification when it's done!

You will have to follow the directions on the website to download the app to your phone... but, basically with one line of code you can do this!

```{r}
library(pushoverr)
pushover("Anthony - your code is done.")
```

