---
title: "Cleaning"
author: "Anthony Gutierrez"
date: "4/19/2021"
output: html_document
---


# Libraries 
```{r}
library(here)
library(tidyverse)
library(tidytext)
library(wordcloud2)
library(janeaustenr)
```

# Introduction
A string and a character are the same thing. You can tell something is a string by the presence of quotations. For example:

words<-"This is a string"
words

# Four Basic Strings 
There are 4 basic families of functions in the {stringr} package:

Manipulation: these functions allow you to manipulate individual characters within the strings in character vectors.
Whitespace tools to add, remove, and manipulate whitespace.
Locale sensitive operations whose operations will vary from locale to locale.
Pattern matching functions. These recognize four engines of pattern description. The most common is regular expressions, but there are three other tools.

Paste words together. This can be useful if say you have a two columns of treatments and you want to combine them into one (e.g., high temp, low temp and high pH, low pH).





Examples:

paste("High temp", "Low pH")
## [1] "High temp Low pH"
Add a dash in between the words

paste("High temp", "Low pH", sep = "-")
## [1] "High temp-Low pH"
Remove the space in between the words

paste0("High temp", "Low pH")
## [1] "High tempLow pH"






## Working with vectors

```{r}
shapes <- c("Square", "Circle", "Triangle")
paste("My favorite shape is a", shapes)
## [1] "My favorite shape is a Square"  
## [2] "My favorite shape is a Circle"  
## [3] "My favorite shape is a Triangle"
two_cities <- c("best", "worst")
paste("It was the", two_cities, "of times.")
## [1] "It was the best of times."  "It was the worst of times."
```

This is very useful when making labels for your plots

Let's say you want to know how long a string is:

```{r}
shapes # vector of shapes
## [1] "Square"   "Circle"   "Triangle"
str_length(shapes) # how many letters are in each word?
## [1] 6 6 8
```

Let's say you want to extract specific characters. Do you work with sequence data? This could be super useful to exact specific bases in a sequence.

```{r}
seq_data<-c("ATCCCGTC")
str_sub(seq_data, start = 2, end = 4) # extract the 2nd to 4th AA
## [1] "TCC"
```








# Modify strings

```{r}
str_sub(seq_data, start = 3, end = 3) <- "A" # add an A in the 3rd position
seq_data
## [1] "ATACCGTC"
```

You can also duplicate patterns in your strings. Here I am duplicating it 2 and 3 times

```{r}
str_dup(seq_data, times = c(2, 3)) # times is the number of times to duplicate each string
## [1] "ATACCGTCATACCGTC"         "ATACCGTCATACCGTCATACCGTC"
```










Say you have a column and you did not copy and paste your treatments like you learned in the first week of class. You now have some words with extra white spaces and R thinks its an entirely new word. Here is how to deal with that...

```{r}
badtreatments<-c("High", " High", "High ", "Low", "Low")
badtreatments
## [1] "High"  " High" "High " "Low"   "Low"


```





# Remove white space
```{r}
str_trim(badtreatments) # this removes both
## [1] "High" "High" "High" "Low"  "Low"

```
You can also just remove from one side or the other

```{r}
str_trim(badtreatments, side = "left") # this removes left
## [1] "High"  "High"  "High " "Low"   "Low"
```


The opposite of str_trim is str_pad, to add white space to either side

```{r}
str_pad(badtreatments, 5, side = "right") # add a white space to the right side after the 5th character
## [1] "High " " High" "High " "Low  " "Low  "
```


add a character instead of white space

```{r}
str_pad(badtreatments, 5, side = "right", pad = "1") # add a 1 to the right side after the 5th character
## [1] "High1" " High" "High " "Low11" "Low11"
```









Important, these will perform differently in different places in the world/with different languages. The default is English, but you can set the language setting.

Make everything upper case
```{r}
x<-"I love R!"
str_to_upper(x)
## [1] "I LOVE R!"
```


Make it lower case
```{r}
str_to_lower(x)
## [1] "i love r!"

```
Make it title case (Cap first letter of each word)

```{r}
str_to_title(x)
## [1] "I Love R!"
```







{stringr} has functions to view, detect, locate, extract, match, replace, and split strings based on specific patterns.

View a specific pattern in a vector of strings.

```{r}
data<-c("AAA", "TATA", "CTAG", "GCTT")
# find all the strings with an A
str_view(data, pattern = "A")
```


{stringr} has functions to view, detect, locate, extract, match, replace, and split strings based on specific patterns.

Detect a specific pattern

```{r}
str_detect(data, pattern = "A")
## [1]  TRUE  TRUE  TRUE FALSE
str_detect(data, pattern = "AT")
## [1] FALSE  TRUE FALSE FALSE
Locate a pattern

str_locate(data, pattern = "AT")
```







Metacharacters: The simplest form of regular expressions are those that match a single character. Most characters, including all letters and digits, are regular expressions that match themselves. For a language like R, there are some special characters that have reserved meaning and they are referred to as ‘Metacharacters”. The metacharacters in Extended Regular Expressions (EREs) are:

. \ | ( ) [ { $ * + ?


Let's say that you have the following set of strings...
```{r}
vals<-c("a.b", "b.c","c.d")
```

And you want to replace all the "." with a space. Here is how you would do it:

```{r}
#string, pattern, replace
str_replace(vals, "\\.", " ")
## [1] "a b" "b c" "c d"
```









Sequences, as the name suggests refers to the sequences of characters which can match. We have shorthand versions (or anchors) for commonly used sequences in R:
Let's subset the vector to only keep strings with digits

```{r}
val2<-c("test 123", "test 456", "test")
str_subset(val2, "\\d")
## [1] "test 123" "test 456"
```


A character class or character set is a list of characters enclosed by square brackets [ ]. Character sets are used to match only one of the different characters. For example, the regex character class [aA] matches any lower case letter a or any upper case letter A.

Let's count the number of lowercase vowels in each string

```{r}
str_count(val2, "[aeiou]")
## [1] 1 1 1
# count any digit
str_count(val2, "[0-9]")
## [1] 3 3 0
```







# Quantifiers
symbol	Meaning
^	Beginning of String
$	End of String
\n	Newline
+	One or More of Previous
*	Zero or More of Previous
?	Zero or One of Previous
{5}	Exactly 5 of Previous
{2, 5}	Between 2 and 5 or Previous
{2, }	More than 2 of Previous





Example: find the phone numbers
         
```{r}
strings<-c("550-153-7578",
         "banana",
         "435.114.7586",
         "home: 672-442-6739")
```

Make a regex that finds all the strings that contain a phone number. We know there is a specific pattern (3 numbers, 3 numbers, 4 numbers and it can have either a "." or "-" to separate them). Let's also say we know that the first number cannot be a 1


```{r}
phone <- "([2-9][0-9]{2})[- .]([0-9]{3})[- .]([0-9]{4})"
```


# Which strings contain phone numbers?
```{r}
str_detect(strings, phone)
```

## [1]  TRUE FALSE  TRUE  TRUE





# Think, Pair, Share
Example: find the phone numbers
# subset only the strings with phone numbers
test<-str_subset(strings, phone)
test
## [1] "550-153-7578"       "435.114.7586"       "home: 672-442-6739"



```{r}
test<-str_subset(strings, phone)
test

```






tidytext
Package for text mining and making text tidy. This is very helpful for social sciences or anyone that uses survey data. Also, really helpful for text mining abstracts to write a review paper on a topic (hint hint: Danielle).

```{r}
# explore it
head(austen_books())

tail(austen_books())
```

Let's clean it up and add a column for line and chapter

```{r}
original_books <- austen_books() %>% # get all of Jane Austen's books
  group_by(book) %>%
  mutate(line = row_number(), # find every line
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]", # count the chapters (starts with the word chapter followed by a digit or roman numeral)
                                                 ignore_case = TRUE)))) %>% #ignore lower or uppercase
  ungroup() # ungroup it so we have a dataframe again
# don't try to view the entire thing... its >73000 lines...
head(original_books)
```

Because we are interest in text mining, we will want to clean this so that there is only one word per row so its tidy. In tidytext each word is refered to as a token. The function to unnest the data so that its only one word per row is unnest_tokens().

```{r}
tidy_books <- original_books %>%
  unnest_tokens(output = word, input = text) # add a column named word, with the input as the text column
head(tidy_books) # there are now >725,000 rows. Don't view the entire thing!
```

OK so we now have >735,000 rows of words.... but, some of these words are kind of useless. Words that are common and don't really have important meaning (e.g. "and","by","therefore"...). These are called stopwords. We can use the function "get_stopwords()" to essentially remove these words from our dataframe. (This function is essentially just a dataframe of unnecessary words)

```{r}
#see an example of all the stopwords
head(get_stopwords())
```


Use what we know from joins to remove all the stopwords

```{r}
cleaned_books <- tidy_books %>%
  anti_join(get_stopwords()) # dataframe
```

without the stopwords
```{r}
## Joining, by = "word"
head(cleaned_books)
```


Let's count the most common words across all her books
```{r}
cleaned_books %>%
  count(word, sort = TRUE)
```








sentiment analysis
There are many ways that we can now analyze this tidy dataset of text. One example is we could do a sentiment analysis (how many positive and negative words) using get_sentiments(). An important note: I was not an English major and I know there are many different lexicons, but I know nothing about them. Look at the help files if you want to go deeper into this...

```{r}
sent_word_counts <- tidy_books %>%
  inner_join(get_sentiments()) %>% # only keep pos or negative words
  count(word, sentiment, sort = TRUE) # count them
```


Now, think about how we could do this with science? Instead of get_sentiments(), you could use an inner_join with a vector of keywords that you are searching for.


# Plot 
We can now use ggplot to visualize counts of positive and negative words in the books
```{r}
sent_word_counts %>%
  filter(n > 150) %>% # take only if there are over 150 instances of it
  mutate(n = ifelse(sentiment == "negative", -n, n)) %>% # add a column where if the word is negative make the count negative
  mutate(word = reorder(word, n)) %>% # sort it so it gows from largest to smallest
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col() +
  coord_flip() +
  labs(y = "Contribution to sentiment")
```





# Make a Word Cloud 
Use the {wordcloud} package to make an interactive word cloud

```{r}
words<-cleaned_books %>%
  count(word) %>% # count all the words
  arrange(desc(n))%>% # sort the words
  slice(1:100) #take the top 100

wordcloud2(words, shape = 'triangle', size=0.3) # make a wordcloud out of the top 100 words
```





# Totally Awesome R package

{ggirl} (gg in real life)
Have you ever made a plot that you love so much and thought, "I want to send this to someone!" Well, now you can! Turn your ggplots into a postcard.
(Note, I wouldn't be mad if random postcards of ggplot showed up in my mailbox...)
