---
title: "Starwars_Group"
author: "Anthony Gutierrez"
date: "4/21/2021"
output: html_document
---
# Introduction and Assignment
Working with intertidal data. Today you will need to use skills that you have learned in working with words to clean up some issues with the character data and use what you learned today to reorder your factors into orders that make sense. (Also the column headers could be better...)

Your goal, as per usual, is to make a plot, any plot where one of the axes is a factor. Save everything in the appropriate folders.

** Please note that script was copied and pasted from partner Alyssa Cohen after my buggy script wouldn't work **


# Libraries
```{r}
library(tidyverse)
library(here)
library(flextable)
library(ggridges)
```


# Data
```{r}
data_dictionary <- read_csv(here("week_12", "Data", "intertidal_data_dictionary.csv"))
data_dictionary %>%
  flextable() %>% 
  theme_booktabs() %>%
  autofit()
```


```{r}
tides <- read_csv(here("week_12", "Data", "intertidaldata.csv"))
lat <- read_csv(here("week_12", "Data", "intertidaldata_latitude.csv"))
```


# clean up the data

only looking at the invertebrates 
```{r}
inverts <- tides %>% select(c(1:3, 11:13)) %>% 
  transform(Quadrat = str_replace_all(Quadrat, "\\.|[0-9]", "")) %>%
  mutate(Quadrat = str_trim(Quadrat), 
         Quadrat = factor(Quadrat, levels = c("Low", "Mid", "High"))) %>%
  rename("Whelks" = "Whelks..Counts.", 
         "Crabs" = "Crabs..Counts.", 
         "Sea Stars" = "Stars..Counts.") %>%
  pivot_longer(cols = c(4:6), 
               names_to = "Invertebrates", 
               values_to = "Count")
unique(inverts$Quadrat)  
```


# Plot

```{r}
inverts %>% 
  filter(Invertebrates == "Crabs", # only grabs
         Count != 0) %>% # remove 0s
  left_join(lat) %>%  # add in latitude to organize
  ggplot(aes(x=Count, 
             y=fct_reorder(Site, Latitude),
             fill=Invertebrates, 
             label= as.character(Latitude))) +
  geom_density_ridges(alpha=0.7) +
  scale_x_continuous(limits = c(0,5.5), 
                     expand = c(0,0)) + 
  labs(y="Site", title="Crabs Found at Each Site") +
  geom_text(aes(label=Latitude, x=5, y=Site), # add latitude labels
            size=2, face="plain", color="gray30") +
  coord_cartesian(clip = "off") + 
  annotate("text", label="Latitude", x=5.5, y=6.7, angle=-90, hjust=0.5) + # add title on right
  theme_classic() +
  theme(legend.position = "none", 
        panel.grid.major.y = element_line(), 
        plot.margin = unit(c(1,2,1,1), "lines"), 
        plot.title.position = "plot") +
  ggsave(here("week_12", "outputs", "Crabs_12b.png"))
```

